\documentclass[12pt,a4paper]{article}
\usepackage[margin=2.5cm]{geometry}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{array}
\usepackage[T1]{fontenc}
\usepackage{parskip}

\hypersetup{
  colorlinks=true,
  urlcolor=blue,
  linkcolor=black
}

\begin{document}

\begin{center}
  {\LARGE\bfseries Data Availability Statement}\\[0.8em]
  {\large Manuscript ID: DD-COM-05-2026-000309}\\[0.4em]
  {\large \textit{Notation Matters: Inconsistency of LLMs in Molecular Representations}}\\[0.4em]
  {\normalsize \textit{Digital Discovery}, Royal Society of Chemistry}\\[1.2em]
  {\normalsize Animesh Mishra \quad|\quad am847@snu.edu.in \quad|\quad ORCID: 0009-0009-1770-6329}\\[0.3em]
  {\normalsize 28 May 2026}
\end{center}

\hrule
\vspace{1.5em}

\section*{Public Repository}

All experimental code, documentation, and article source are publicly available \textbf{without embargo} at:

\begin{center}
  \url{https://github.com/amethystani/notation-matters}
\end{center}

No authentication is required. The repository is licensed under the MIT License.

\section*{Available Artifacts}

\subsection*{Experimental Scripts}

\begin{description}
  \item[\texttt{07\_full\_esol\_phase1.py}] Phase 1 --- notation consistency evaluation across four molecular representations (SMILES, IUPAC, InChI, SELFIES) on 1072 molecules from the ESOL dataset.

  \item[\texttt{08\_full\_esol\_phase2.py}] Phase 2 --- Ridge regression pooling of per-notation prediction heads; produces regression coefficients and cross-fold validation metrics.

  \item[\texttt{run\_full\_benchmark.sh}] Batch pipeline that executes both phases sequentially with consistent random seeds.
\end{description}

\subsection*{Documentation and Article Source}

\begin{itemize}
  \item \texttt{README.md} --- Installation instructions, usage guide, and reproducibility notes
  \item \texttt{main.tex} --- Complete 6-page LaTeX article source (Communication format)
  \item \texttt{rsc.bib} --- Bibliography file with all DOIs verified
  \item \texttt{DATA\_AVAILABILITY\_STATEMENT.md} --- Machine-readable version of this statement
\end{itemize}

\subsection*{Source Dataset}

Ground-truth aqueous solubility values ($\log S$) are from the publicly available ESOL dataset:

\begin{itemize}
  \item Delaney, J.\,S. \textit{J.\ Chem.\ Inf.\ Comput.\ Sci.} \textbf{2004}, \textit{44}(3), 1000--1005.
  \item DOI: \url{https://doi.org/10.1021/ci034243x}
\end{itemize}

IUPAC names and InChI identifiers are retrieved at runtime via the PubChem REST API (\url{https://pubchem.ncbi.nlm.nih.gov/}).

\section*{Accessibility Summary}

\vspace{0.5em}
\begin{tabular}{>{\bfseries}lp{10cm}}
  \toprule
  Public access & Yes --- no login or request required \\
  Embargo & None \\
  Usage restrictions & None (MIT License) \\
  Persistent URL & \url{https://github.com/amethystani/notation-matters} \\
  Archived results & Generated at runtime by executing provided scripts \\
  External dataset & ESOL via Delaney (2004), retrieved via PubChem REST API \\
  \bottomrule
\end{tabular}
\vspace{0.5em}

\section*{Reproducibility Notes}

\begin{itemize}
  \item LLM inference uses Qwen3.6 via Ollama; minor numerical variation is possible across hardware configurations.
  \item All statistical tests (Fisher exact, Kruskal-Wallis, Mann-Whitney U, Wilcoxon signed-rank) use fixed random seeds for deterministic reproduction.
  \item 56 of 1128 ESOL molecules are excluded due to missing PubChem IUPAC entries; final dataset comprises 1072 molecules.
  \item 89.4\% of SMILES strings yield valid SELFIES representations; the remainder are excluded from SELFIES analyses.
\end{itemize}

\section*{Contact}

Queries regarding code execution or reproducibility will be addressed within five business days:

\begin{center}
  Animesh Mishra \quad \texttt{am847@snu.edu.in}\\
  School of Engineering, Shiv Nadar Institution of Eminence\\
  \url{https://orcid.org/0009-0009-1770-6329}
\end{center}

\vspace{2em}
\hrule
\vspace{1em}

\noindent\textit{I certify that all data and code referenced in the manuscript are publicly accessible at the repository above, without embargo or conditions of access, as of 28 May 2026.}

\vspace{1.5em}
\noindent\textbf{Animesh Mishra}\\
28 May 2026

\end{document}
